### 2017-03-01 paper/chapters/sigmoid_belief_nets.tex
fixed formulation to be conservative

Sigmoid Belief Networks (SBN) were proposed in 1992 by R.M. Neal \cite{neal:1992} representing a specific type of bayesian networks \cite{pearl:1985} shown in figure \ref{fig:sbn_arch}
In the case of SBNs however, all states are binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modeling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variable in the bayesian framework which means it can be observed, hidden or unknown representing different states of knowledge. As such it can also be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
\end{equation}
where 
\begin{conditions}
  \sigma(x) & $\frac{1}{1 + e^{-x}}$ (sigmoid function)\\
  W_{j,i} & connection weights from state $s_j$ to $s_i$\\
\end{conditions}

>>>>

Sigmoid Belief Networks (SBN) were described in 1992 by R.M. Neal \cite{neal:1992} representing a specific type of bayesian networks \cite{pearl:1985} shown in Figure \ref{fig:sbn_arch}
In the case of SBNs however, all states are binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modeling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variable in the bayesian framework which means it can be observed, hidden or unknown representing different states of knowledge. As such it can also be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
\end{equation}
where 
\begin{conditions}
  \sigma(x) & $\frac{1}{1 + e^{-x}}$ (sigmoid function)\\
  W_{j,i} & connection weights from state $s_j$ to $s_i$\\
\end{conditions}
